Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-27 presentations/bsa_2020-07-27/index.Rmd
Update slides
- Add Gotelli 2000 ref
- Add data source for conservation areas

Null distribution: 999 communities randomized using "Independent Swap" (Gotelli, 2000)

@@

ggplot() +
  geom_sf(data = japan) +
  geom_sf(data = protected_areas, aes(fill = status), color = "transparent") +
  coord_sf(xlim = c(japan_box$xmin, japan_box$xmax), ylim = c(japan_box$ymin, japan_box$ymax)) +
  labs(
    fill = "Conservation\nstatus"
  ) +
  scale_fill_viridis_d(breaks = names(status_labels), labels = status_labels) +
  theme(
    axis.ticks = element_blank()
  )
```

>>>>

Null distribution: 999 communities randomized using "Independent Swap" `r AutoCite(bib, "Gotelli2000")`

@@

ggplot() +
  geom_sf(data = japan) +
  geom_sf(data = protected_areas, aes(fill = status), color = "transparent") +
  coord_sf(xlim = c(japan_box$xmin, japan_box$xmax), ylim = c(japan_box$ymin, japan_box$ymax)) +
  labs(
    fill = "Conservation\nstatus"
  ) +
  scale_fill_viridis_d(breaks = names(status_labels), labels = status_labels) +
  theme(
    axis.ticks = element_blank()
  ) + 
  labs(
    caption = "Data: Japan Ministry of the Environment\nhttps://www.biodic.go.jp/biodiversity/activity/policy/map/map17/"
  )
```
